Breast Cancer Diagnosis Classification Analysis

### 2022-12-05 powerpoint.rmd

---
title: "Characterizing breast cancer cells"
author: Austin Lackey, Ethan Powers and Danny Laposata
date: Friday, November 9th, 2022
output: powerpoint_presentation
---

## The data

- We have a dataset of 569 breast cancer cells, some of which are cancerous and some of which are benign.
- We have 30 features for each cell, which are the measurements of the cell.
- We have a binary variable, `diagnosis`, which is `M` for malignant and `B` for benign.
- Add more stuff here...

## Sample Output
```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(caret)
set.seed(420)
data <- read.csv("breast_cancer_diagnostic_data.csv")
data <- subset(data, select = -c(X))
split <- sample(c(rep(0, 0.6 * nrow(data)), rep(1, 0.4 * nrow(data))))
train <- data[split == 0, ]
test <- data[split== 1, ]
#write.csv(train,"training.csv", row.names = FALSE)
#write.csv(test,"test.csv", row.names = FALSE)
```

# Exploratory Data Analysis

# Model Building

# Testing Accuracy

>>>>

---
title: "Breast Cancer Diagnosis Classification Analysis"
author: Austin Lackey, Ethan Powers and Danny Laposata
date: "December 9th, 2022"
output: 
  powerpoint_presentation: 
    reference_doc: template.pptx

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## Background

- Breast Cancer Diagnosis Data
- Predict Diagnosis of Tumor based on features
- Reduce Type II Error (False-Negatives)
- Feature Selection

## Data

- Data collected from Kaggle
- Response: Diagnosis (Benign/Malignant)
- Mean, SE, and "Worst" measurements of 10 variables
- Training/Test Split (60/40)

## EDA

- Different measurements of each variable are correlated

- Relationship with Diagnosis visible for each measurement

```{r, fig.height=3, fig.width=4, fig.align='right', fig.pos='H'}
source("Danny's Analysis.R", echo = F, local = T)

train[,c(1,2,12,22)] |>
  ggpairs(title = "Correlation b/w Radius Measurements")
```

## Classification Analysis: Austin

## Classification Analysis: Danny

## Regression Analysis: Ethan

## Model Assesments
